External validation

### 2020-11-30 diagnostics/README.Rmd

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  github_document:
    toc: yes
    df_print: "kable"
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

>>>>

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
#  github_document:
#    toc: yes
#    df_print: "kable"
  html_document:
    toc: yes
    df_print: "kable"
    toc_float: yes
    number_sections: yes
    code_folding: "hide"
    keep_md: yes
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---
